\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemSkills}[2]{
  \item\normalsize{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemExperience}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubheadingEducation}[5]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5}\\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheadingProject}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
    %   \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubItemSkills}[2]{\resumeItemSkills{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListStartSkillsAwards}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\Huge Prayuj Tuli} & Email : \href{mailto:}{prayujtuli@gmail.com}\\
%   & Mobile : +1-813-892-2714 \\
%   & GitHub : \href{http://github.com/prayujt}{prayujt} \\
%   & LinkedIn : \href{http://linkedin.com/in/prayuj-tuli}{prayuj-tuli} \\
% \end{tabular*}

% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \centerline{\textbf{\huge Prayuj Tuli}}\vspace{0.15cm}
    \centerline{Email : \href{mailto:}{prayujtuli@gmail.com} $|$
    Mobile : 813-892-2714 $|$
    GitHub : \href{http://github.com/prayujt}{prayujt} $|$
    LinkedIn : \href{http://linkedin.com/in/prayuj-tuli}{prayuj-tuli}}
% \end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {B.S in Computer Science \& B.S. in Mathematics; GPA: 3.97/4.00}{Aug 2021 -- Dec 2024}
    \resumeItemListStart
        \resumeItem{Relevant Coursework}
            {Data Structures and Algorithms, Linear Algebra, Compilers, Probability, Databases, Differential Equations, Discrete Mathematics, Statistics, Proofs}
    \resumeItemListEnd
    \resumeSubheading
      {Land O' Lakes High School}{Land O' Lakes, FL}
      {International Baccalaureate Program; Valedictorian - GPA: 4.81/4.00}{Aug 2017 -- May 2021}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Florida}{Gainesville, FL}
      {Teaching Assistant: COP3530 - Data Structures and Algorithms}{Aug 2022 -- Present}
      \resumeItemListStart
        \resumeItemExperience
          {Conducting biweekly office hours to assist students in learning course content.}
        \resumeItemExperience
          {Involved in grading student coursework such as exams and projects.}
        \resumeItemExperience
          {Working with professors to automate grading workflow using the Google Sheets and Canvas APIs.}
        \resumeItemListEnd

    \resumeSubheading
      {KUMON}{Lutz, FL}
      {Math/Reading Instructor}{Aug 2019 -- April 2020}
      \resumeItemListStart
        \resumeItemExperience
            {Worked part-time during the school year helping younger kids become proficient in higher level algebra and improve their reading comprehension.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd

%-----------Activities-----------------
\section{Involvement}
    \resumeSubHeadingListStart
      \resumeSubheading
        {Open Source Club}{Gainesville, FL}
        {Technical Lead}{Aug 2022 -- Present}
        \resumeItemListStart
          \resumeItemExperience
            {Leading ``Casual Coding'' sessions to work with and assist members on open-source projects.}
          \resumeItemExperience
            {Responsible for management of club's public Git repositories.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Projects-----------------
\section{Projects}
  \resumeSubHeadingListStart
    % \resumeSubHeadingListStart
        \resumeSubheadingProject
          {You Owe Me}{June 2022 -- Aug 2022}
          \resumeItemListStart
            \resumeItemExperience
              {Worked as a group to simplify the process of paying back debts between multiple people by significantly reducing the number of edges in a weighted directed graph.}
          \resumeItemListEnd
        \resumeSubheadingProject
          {Subsonic Streaming}{May 2022 -- Aug 2022}
          \resumeItemListStart
            \resumeItemExperience
              {Self-hosted a music streaming server for personal use through Subsonic's open-source software.}
            \resumeItemExperience
              {Integrated with Apple Shortcuts' SSH functionalities to easily use features such as adding new songs, replacing existing songs with different audio sources, and migrating public Spotify playlists.}
            \resumeItemExperience
              {Utilized Subsonic's Python API to allow for back-end communication with the music server, Spotify's API to gather song metadata, and other libraries to properly set .mp3 file ID3 tags.}
          \resumeItemListEnd
        \resumeSubheadingProject
          {Arch Linux}{Aug 2021 -- Present}
          \resumeItemListStart
            \resumeItemExperience
              {Configured an Arch Linux environment from scratch to optimize work productivity through custom keyboard macros and efficient window tiling, while creating an aesthetically clean display.}
            \resumeItemExperience
              {Wrote several Bash and Python scripts to personalize the environment, including adding facial recognition for PAM authentication, and offline voice recognition to control the device.}
            \resumeItemExperience
              {Applied Xorg's C++ libraries to write low-level programs to handle raw input events and synchronize with RGB lights using OpenRGB.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
          
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStartSkillsAwards
   \resumeSubItemSkills{Languages}{C++, Python, Java, NodeJS, Bash, LaTeX, SQL}
    \resumeSubItemSkills{Technologies}{Git, Linux, Vim, Emacs, Microsoft Office}
 \resumeSubHeadingListEnd

%-----------AWARDS-----------------
\section{Awards}
  \resumeSubHeadingListStartSkillsAwards
    \resumeSubItemSkills{National Merit Finalist}
      {Scored in the 99th percentile on the PSAT}
    \resumeSubItemSkills{University of Florida Dean's List}
      {Herbert Wertheim College of Engineering (2021-2022)}
    % \resumeSubItemSkills{Microsoft Excel (Office 2019) Certification}{Score: 975/1000}
  \resumeSubHeadingListEnd

\end{document}
